\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 metatheory-condensed.tex
rewording

\item
\TT also features \emph{linkage transformers} that enable inductive
construction of linkages (and thus families): a linkage can be constructed by inheriting or
overriding components of an existing linkage, or by extending an existing
linkage with new components.

>>>>

\item
\TT also features a set of \emph{linkage transformers} that enable inductive
construction of families: a linkage can be constructed by inheriting or
overriding components of an existing linkage, or by extending an existing
linkage with new components.
